The first high-redshift Changing Look Quasars

### 2019-11-14 tex/CIV_CLQs.tex
plots/spectral/CIV_fits_1comp.png and CIV_fits_2comp.png added

For J1205+3422, our spectral observations cover 5195 days observed, 1691 days
in the rest-frame. For J1205+3422 is identified in SDSS as a bright
$g\approx18.0$, blue-sloped quasar with broad \siiv, \civ, \ciii and
\mgii observed in the initial spectrum (MJD 53498; 2005-May-08). \ciii
and \civ\ are seen to have large blueshifts of $\approx$2600$\pm$150
and $\approx$1150$\pm$100 km s$^{-1}$, respectively.  By the time the
2019 spectra were taken (MJD 58538, 2019-Feb-24 and MJD 58693
2019-Jul-29), however, the light curve has dropped by $\sim$1.5
magnitudes and the spectra are significantly less steep.  While \lya
and \nv are detectable in both the MJD 58538 and MJD 58693 DBSP
spectra, \civ\ has all but disappeared in the MJD 58693 spectrum.  The
broad \ciii emission has disappeared between the 2005 and 2019
spectra. {\it The changes in \civ\ and \ciii going from broad emission to
barely detectable have on the timescales of $\approx$50 days in the rest-frame.}

>>>>

For J1205+3422, our spectral observations cover 5195 days observed,
1691 days in the rest-frame. This quasar was initially identified in
SDSS in 2005 May, as a bright, $g\approx18.0$, blue-sloped quasar with
broad \siiv, \civ, \ciii and \mgii. \ciii and \civ\ have large
blueshifts of $\approx$2600$\pm$150 and $\approx$1150$\pm$100 km
s$^{-1}$, respectively.  By 2019, however, the opitical brightness
dropped by $\sim$1.5 magnitudes and the spectra are significantly less
blue.  While \lya and \nv are detectable in both 2019 spectra, \civ\
has all but disappeared in the 2019 June spectrum.  The broad \ciii
emission has disappeared between the 2005 and 2019 spectra. The
changes in \civ\ and \ciii going from broad emission to barely
detectable have on the timescales of $\approx$50 days in the
rest-frame.
